### 2020-04-15 serial.tex
changes in order

Characterizing generation- and serial-interval distributions are critical to understanding the outset of an outbreak as they determine the time scale of disease transmission.
Generation intervals measure the time difference between infection of a transmission pair, whereas serial intervals measure the time difference between symptom onset of a transmission pair.
Due to their similar definitions, there differences have been inaccurately captured and misunderstood.
We provide a theoretical basis for understanding serial intervals and show that both generation and serial intervals provide a correct link between $r$ and $\mathcal R$.
Our analysis further reveals gap in current understanding and practical approaches to studying serial intervals.

@@

Using cohort-based approaches, we define forward and backward serial intervals.
The forward serial-interval distribution describes the renewal process of the

>>>>

Characterizing generation- and serial-interval distributions are critical to understanding the outset of an outbreak as they determine the time scale of disease transmission.
Generation intervals measure the time difference between infection of a transmission pair, whereas serial intervals measure the time difference between symptom onset of a transmission pair.
Due to their similar definitions, there differences have been inaccurately captured and misunderstood.
Here, we provide a theoretical basis for understanding serial intervals.

@@

Using cohort-based approaches, we define forward and backward serial intervals.
The forward serial-interval distribution describes the renewal process of the symptomatic cases and therefore provides the correct link between $r$ and $\mathcal R$.
While our results support the use of serial interval distributions for calculating $\mathcal R$, 
they also reveal gaps in our current understanding and practical approaches to characterizing serial intervals.
